---
title: "Assignment 3: Data wrangling"
author: "Your Name"
date: "Today's date"
output: html_document
---

**Due Sunday, October 30, 2022 @ 11:59pm through Github**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

(1) Read in the unprocessed NMES data (`nmesUNPROC.csv`) using the `read_csv()` function. Store this data in an object called `nmesRAW`.

```{r}
#Put your code to read in the data here

```

(2) Add an `mscd` factor variable to the dataset that is an indicator of whether the individual has a major smoking caused disease (1 = Yes, 0 = No).  You can create this variable from the `lc5` and `chd5` variables as we did in class. (See Content 3-3 for hints.)

```{r}
#Put your code for this here

```

(3) Recode the categorical variables in the NMES data into factors according to the following codebook.  Once all of your recoding is complete and you've dropped any intermediate variables, rename the dataset `nmesPROC`.


```{r}
#Put your code for this here

```

(4) Give the code needed to create the following new variables and add them to your dataset:

```{r}
#Put your code for this here
```

