---
title: "Assignment 3: Data wrangling"
author: "Your Name"
date: "Today's date"
output: html_document
---

**Due Sunday, October 27, 2019 @ 11:59pm through Github**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

(1) Read in the unprocessed NMES data (`nmesUNPROC.csv`) using the `read_csv()` function. Store this data in an object called `nmesRAW`.

```{r}
#Put your code to read in the data here

```

(2) Add an `mscd` factor variable to the dataset that is an indicator of whether the individual has a major smoking caused disease (1 = Yes, 0 = No).  You can create this variable from the `lc5` and `chd5` variables as we did in class. (See class work 3-3 for hints.)

```{r}
#Put your code for this here

```

(3) Recode the categorical variables in the NMES data into factors according to the following codebook.  Once all of your recoding is complete, drop the original variables and rename the dataset `nmesPROC`.


```{r}
#Put your code for this here

```

(4) Give the code need to do the asked for recodings:

```{r}
#Put your code for this here
```

